Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-03-21 draftfinalreport_v2.Rnw
Tidying and revisions
Eg relevel for the regression

## use tpsub
#hist(tpsub$cases,xlab="Cases",main='Histogram of cases per category',col="darkgrey",breaks=20)

@@

resan<-xtable(anova(model3,test="F"))
#resan<-xtable(anova(model2,test="F"))
# print(resan,floating = FALSE)

#xtb<-xtable(summary(model3))
xtb<-xtable(summary(model2))
# print(xtb,floating = FALSE)

@@

# proportions of the naive population the wuld be covered if vaccinated by age groups now
propvCohort<-c(
round((sum(naive$Naive[3:6])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:12])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:30])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:45])/sum(naive$Naive)),2),
round((sum(naive$Naive[8:100])/sum(naive$Naive)),2))
names(propvCohort)<-c("2-5","5-11","5-16","5-18","11-16","11-18","0-29","0-44",">8")
write.table(propvCohort,"vaccine_proportions_Cohort.txt",sep=",",row.names=T,col.names=F)

propsv = NULL
for (i in 1:20 ) {
  propsv[i] = round((sum(naive$Naive[i:13])/sum(naive$Naive)),2)
}
propsvAge = NULL
for (i in 1:20 ) {
  propsvAge[i]=paste(c(min(i:20)-1, max(i:20)-1),collapse="-")
}

@@

vacp<-read.csv("vacc_predictions.csv",header=T)
hosp<-read.csv("hospital.csv",header=T)
resan<-xtable(anova(model3,test="F"))
xtb<-xtable(summary(model3))

@@

\begin{table}[hbtp]\scriptsize
<<results=tex,echo=FALSE>>=# This chunk uses "results=tex"
latex(ttyr, file="",table.env=FALSE,rowname=NULL)
@
\caption{Absolute number of measles cases with no ethnicity recorded for specific age and socio-economic deprivation (NZDep) categories from 2007-2014.}
\label{table:none}
\end{table}

@@

\begin{table}[hbtp]\scriptsize
\caption{Per capita measles rates}
<<results=tex,echo=FALSE>>=
latex(PerCap, file="", table.env=FALSE,rowname=NULL)
@
\label{table:percap_rates}
\end{table}

\begin{table}[hbtp]\footnotesize
\caption{Proportions of the naive population the would be covered if vaccinated by age groups}
<<results=tex,echo=FALSE>>=
latex(propvCohort, file="", table.env=FALSE)
@
\label{table:vaccine_cohort}
\end{table}

@@

\begin{table}[hbtp] \scriptsize
\caption{Measles cases (Cases), population sizes (Population) and per capita rates per 10,000 (Per capita) of measles in specific age (Age), ethnicity (Ethnicity) and socio-economic deprivation (NZDep) categories from 2007-2014}
<<results=tex,echo=FALSE>>=
latex(PerCap, file="", table.env=FALSE,rowname=NULL)
@
\label{table:percap}
\end{table}

@@

\begin{figure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{naive_au.pdf}
\end{center}
\caption{New Zealand population by age and estimated numbers of na\"{\i}ve people in each age class using National Immunisation Register level data and national census data as the denominator}
\label{fig:naive_au}
\end{figure}

@@

\begin{sidewaysfigure}[H]
      \centering
     \includegraphics[width=0.9\textwidth]{cases_by_dhb_2009_2014.pdf}
     \caption{Measles cases by District Health Board (DHB) from 2009 to 2014}
     \label{fig:dhbcases}
\end{sidewaysfigure}

\begin{sidewaysfigure}[H]
     \centering
     \includegraphics[width=0.9\textwidth]{outbreaks_2009_2014.pdf}
     \caption{Measles data classified as outbreaks for reproduction number of the infection ($R_v$) estimation from 2009 to 2014}
     \label{fig:outbreaks}
\end{sidewaysfigure}

\begin{sidewaysfigure}[H]
     \centering
     \includegraphics[width=0.9\textwidth]{averageR0_all_ob.pdf}
     \caption{Estimates of $R_v$ for the outbreaks each year, as classified by outbreaks in \autoref{fig:outbreaks}. Sporadic cases are excluded.}
     \label{fig:r0}
\end{sidewaysfigure}

@@

<<results=tex,echo=FALSE>>=
colnames(vacp) <- c("Age range", "Proportion")
latex(vacp, file="", table.env=FALSE,rowname=NULL)
@
\label{table:vacp}
\end{sidewaystable}

>>>>

## use tpsub
#hist(tpsub$cases,xlab="Cases",main='Histogram of cases per category',col="darkgrey",breaks=20)
tpsub$Ethnicity<- relevel(tpsub$Ethnicity, "European")

@@

resan<-xtable(anova(model3,test="F"))
xtb<-xtable(summary(model3))

@@

# proportions of the naive population the wuld be covered if vaccinated by age groups now
propvCohort<-c(
round((sum(naive$Naive[3:6])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:12])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:30])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:45])/sum(naive$Naive)),2),
round((sum(naive$Naive[8:100])/sum(naive$Naive)),2))
yr_range<-c("2-5","5-11","5-16","5-18","11-16","11-18","0-29","0-44",">8")
propvCohort<-cbind(yr_range,propvCohort)
propvCohort<-as.data.frame(propvCohort)
write.table(propvCohort,"vaccine_proportions_Cohort.txt",sep=",",row.names=T,col.names=F)
propsv = NULL
for (i in 1:20 ) {
  propsv[i] = round((sum(naive$Naive[i:13])/sum(naive$Naive)),2)
}
propsvAge = NULL
for (i in 1:20 ) {
  propsvAge[i]=paste(c(min(i:20)-1, max(i:20)-1),collapse="-")
}

@@

vacp<-read.csv("vacc_predictions.csv",header=T)
hosp<-read.csv("hospital.csv",header=T)

@@

% \begin{table}[hbtp]\scriptsize
% <<results=tex,echo=FALSE>>=# This chunk uses "results=tex"
% latex(ttyr, file="",table.env=FALSE,rowname=NULL)
% @
% \caption{Absolute number of measles cases with no ethnicity recorded for specific age and socio-economic deprivation (NZDep) categories from 2007-2014.}
% \label{table:none}
% \end{table}

@@

% \begin{table}[hbtp]\scriptsize
% \caption{Per capita measles rates}
% <<results=tex,echo=FALSE>>=
% latex(PerCap, file="", table.env=FALSE,rowname=NULL)
% @
% \label{table:percap_rates}
% \end{table}

\begin{table}[hbtp]\footnotesize
\caption{Proportions of the na\"{\i}ve population the would be covered if vaccinated by age groups}
<<results=tex,echo=FALSE>>=
colnames(propvCohort) <- c("Age range", "Proportion")
latex(propvCohort, file="", table.env=FALSE,rowname=NULL)
@
\label{table:vaccine_cohort}
\end{table}

@@

\begin{table}[hbtp] \scriptsize
\caption{Measles cases (Cases), population sizes (Population) and per capita rates per 10,000 (Per capita) of measles in specific age (Age), ethnicity (Ethnicity) and socio-economic deprivation (NZDep) categories from 2007-2014}
<<results=tex,echo=FALSE>>=
colnames(PerCap)<-c("NZDep","Age","Ethnicity","Population","Cases","Per capita")
latex(PerCap, file="", table.env=FALSE,rowname=NULL)
@
\label{table:percap}
\end{table}

@@

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{naive_au.pdf}
\end{center}
\caption{New Zealand population by age and estimated numbers of na\"{\i}ve people in each age class using National Immunisation Register level data and national census data as the denominator}
\label{fig:naive_au}
\end{sidewaysfigure}

@@

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{cases_by_dhb_2009_2014.pdf}
          \end{center}
\caption{Measles cases by District Health Board (DHB) from 2009 to 2014}
     \label{fig:dhbcases}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{outbreaks_2009_2014.pdf}
     \end{center}
     \caption{Measles data classified as outbreaks for reproduction number of the infection ($R_v$) estimation from 2009 to 2014}
     \label{fig:outbreaks}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\begin{center}
     \includegraphics[width=0.9\textwidth]{averageR0_all_ob.pdf}
     \end{center}
     \caption{Estimates of $R_v$ for the outbreaks each year, as classified by outbreaks in \autoref{fig:outbreaks}. Sporadic cases are excluded.}
     \label{fig:r0}
\end{sidewaysfigure}

@@

<<results=tex,echo=FALSE>>=
latex(vacp, file="", table.env=FALSE,rowname=NULL)
@
\label{table:vacp}
\end{sidewaystable}
